Defining Crete's Macroecology based on its soil Microbial Interactome

### 2023-12-23 manuscript.tex
add more refs and draft text in intro

The island of Crete, Greece has been studied since the classical times for its' fauna \citep{Sidiropoulos_Polymeni_Legakis_2017}, flora \citep{Krimbas_2005} and ecosystems \citep{Grove1993}.

The introduction introduces the context and summarizes the manuscript. It is importantly to clearly state the contributions
of this piece of work. Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

This is an example of a new parapgraph with a numbered footnote\footnote{\url{https://data.gov.uk/}} and a second footnote marker.\footnote{Example of footnote text.}

>>>>

The island of Crete, Greece has been studied since the classical times for its' fauna \citep{Sidiropoulos_Polymeni_Legakis_2017}, flora \citep{Krimbas_2005} and ecosystems \citep{Grove1993}.
Crete is a continental island, fifth largest island of the mediterranean, a mediterranean biodiversity hotspot, model for desertification and climate change, elevation gradient, grasing impacts on ecosystems and evolutionary model.
Yet the terrestrial microbial diversity has been unexplored.

Has been sampled from major worldwide projects of microbiome studies.

Global soil microbiome studies \citep{Delgado-Baquerizo2018} and \citep{Bahram2018} and the biogeography \citep{Martiny2006} \citep{Guerra2020}, \citep{Labouyrie2023} yet there are significant blind spots \citep{Guerra2020}. The most resolute study is \citep{Karimi2020}

Islands are nature's labs \citep{Whittaker2017} and in soil microbes \citep{Li2020} and fungi \citep{Delavaux2021}
Ultimately islands can set the ground to represent ecosystems with data and complex interactions \citep{Davies2016}.

Genome Standards Consortium, FAIR data, unrestricted, rich metadata

Here we present

%This is an example of a new parapgraph with a numbered footnote\footnote{\url{https://data.gov.uk/}} and a second footnote marker.\footnote{Example of footnote text.}
